Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-19 paper/Paper.tex
remove emergencyClose from interface

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minTokensToCreate,
        uint _closingTime,
        address _privateCreation
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function emergenyCloseProposal(uint _proposalID) external;
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);

>>>>

    function DAO(
        address _curator,
        DAO_Creator _daoCreator,
        uint _proposalDeposit,
        uint _minTokensToCreate,
        uint _closingTime,
        address _privateCreation
    )
    function () returns (bool success);
    function receiveEther() returns(bool);
    function newProposal(
        address _recipient,
        uint _amount,
        string _description,
        bytes _transactionData,
        uint _debatingPeriod,
        bool __newCurator
    ) onlyTokenholders returns (uint _proposalID);
    function checkProposalCode(
        uint _proposalID,
        address _recipient,
        uint _amount,
        bytes _transactionData
    ) constant returns (bool _codeChecksOut);
    function vote(
        uint _proposalID,
        bool _supportsProposal
    ) onlyTokenholders returns (uint _voteID);
    function executeProposal(
        uint _proposalID,
        bytes _transactionData
    ) returns (bool _success);
    function splitDAO(
        uint _proposalID,
        address _newServiceProvider
    ) returns (bool _success);
    function newContract(address _newContract);
    function changeAllowedRecipients(address _recipient, bool _allowed) external returns (bool _success);
    function changeProposalDeposit(uint _proposalDeposit) external;
    function retrieveDAOReward(bool _toMembers) external returns (bool _success);
    function getMyReward() returns(bool _success);
    function withdrawRewardFor(address _account) returns(bool _success);
    function transferWithoutReward(address _to, uint256 _amount) returns (bool success);
    function transferFromWithoutReward(
        address _from,
        address _to,
        uint256 _amount
    ) returns (bool success);
    function halveMinQuorum() returns (bool _success);
    function numberOfProposals() constant returns (uint _numberOfProposals);
    function getNewDAOAdress(uint _proposalID) constant returns (address _newDAO);
    function isBlocked(address _account) returns (bool);
